### 2021-06-09 paper/report.tex
Formatting.
Add missing references.

We include two types of tests. Polymerase chain reaction (PCR) tests directly reveal
whether an individual is infected or not. PCR tests require some days to be processed
and there are always aggregate capacity constraints. In contrast, rapid antigen tests
yield immediate results. Specificity and sensitivity of these tests is set according to
data analysed in \cite{Bruemmer2021, Smith2021}; sensitivity depends on the timing of
the test relative to the start of infectiousness. Figure~\ref{fig:antigen_tests} shows
our model for rapid test demand. Schools may require students to be tested regularly.
Rapid tests may be offered by employers for on-site workers. Individuals may demand
tests for private reasons, which include having plans to meet other people\footnote{A
positive test will make them reduce their contacts; this is why tests impact the actual
contacts in Figure~\ref{fig:model-description}.}, showing symptoms of CoViD-19, and
because a household member tested positively for the virus. We endow each agent with an
individual compliance parameter. This parameter determines whether she takes up rapid
tests offered by employers or follows up on private reasons. Thresholds differ across
reasons triggering rapid test demand; they are lowest for infected household members and
highest for meeting other people.\comment[id=HM]{True?}.

@@

We apply this model to Germany. In March and April 2020, the country broke the first
wave of the pandemic fairly quickly. Between mid-May and mid-September, daily new
infections were below 20 per Million and day.\comment[id=HM]{Cite our world in data} We
model the period mid-September 2020 to the end of May 2021. We pick the starting date
for two reasons. First, we do not include the first wave because the environment was
very different (e.g., aggregate PCR test capacity was much lower and we would require a
very different model for calculating the share of known cases) Second, a large fraction
cases during summer of 2020 were traced to international travel
\citep{KochInstitut2021}\comment[id=HM]{Include
\url{https://www.nature.com/articles/s41586-021-03677-y} in citation}, but the precise
number is difficult to model.

>>>>

We include two types of tests. Polymerase chain reaction (PCR) tests directly reveal
whether an individual is infected or not. PCR tests require some days to be processed
and there are always aggregate capacity constraints. In contrast, rapid antigen tests
yield immediate results. Specificity and sensitivity of these tests is set according to
data analysed in \cite{Bruemmer2021, Smith2021}; sensitivity depends on the timing of
the test relative to the start of infectiousness. Figure~\ref{fig:antigen_tests} shows
our model for rapid test demand. Schools may require students to be tested regularly.
Rapid tests may be offered by employers for on-site workers. Individuals may demand
tests for private reasons, which include having plans to meet other people\footnote{A
    positive test will make them reduce their contacts; this is why tests impact the actual
    contacts in Figure~\ref{fig:model-description}.}, showing symptoms of CoViD-19, and
because a household member tested positively for the virus. We endow each agent with an
individual compliance parameter. This parameter determines whether she takes up rapid
tests offered by employers or follows up on private reasons. Thresholds differ across
reasons triggering rapid test demand; they are lowest for infected household members and
highest for meeting other people.\comment[id=HM]{True?}\comment[id=K]{FALSE. We only have one private demand threshold (over time) which is the same for own symptoms and no PCR test, household member with symptoms or positive test and for having a weekly meeting with friends.}.

@@

We apply this model to Germany. In March and April 2020, the country broke the first wave
of the pandemic fairly quickly. Between mid-May and mid-September, daily new infections
were below 20 per Million and day.\comment[id=HM]{Cite our world in data} We model the
period mid-September 2020 to the end of May 2021. We pick the starting date for two
reasons. First, we do not include the first wave because the environment was very
different (e.g., aggregate PCR test capacity was much lower and we would require a very
different model for calculating the share of known cases) Second, a large fraction cases
during summer of 2020 were traced to international travel
\citep{KochInstitut2021,Hodcroft2021} but the precise number is difficult to model.
